MISUSES AND INACCURACIES OF PAGEL'S LAMBDA ML ESTIMATION METHODS

### 2020-04-23 Manuscript/Manuscript-2.tex
vsn 2

\hypertarget{estimates-of-phylogenetic-signal-based-on-lambda-are-often-inaccurate}{%
\section{Estimates of Phylogenetic Signal Based on Lambda are Often
Inaccurate}\label{estimates-of-phylogenetic-signal-based-on-lambda-are-often-inaccurate}}

@@

\textbf{Keywords}: Pagel's lambda, phylogenetic signal \hfill\break

\textbf{Short Title}: Inaccuracies in Pagel's Lambda \hfill\break

@@

For many macroevolutionary analyses, it is often of interest to quantify
the degree to which phylogenetic signal is displayed in continuous
traits. Several analytical tools have been developed for this purpose
(e.g., Gittleman and Kot 1990; Abouheif 1999; Pagel 1999; Blomberg et
al. 2003; Klingenberg and Gidaszewski 2010; Adams 2014a), which differ
primarily in how they characterize the phylogenetic dependency of trait
variation among taxa. One commonly used statistical measure,
\emph{Kappa} (\(K\)), expresses the strength of phylogenetic signal as
the ratio of observed trait variation to the trait variation conditioned
on the phylogeny; scaled by what is expected under Brownian motion given
the phylogeny's size and shape (Blomberg et al. 2003; also Adams 2014a).
Another approach, Pagel's \(\lambda\) (Pagel 1999), uses maximum
likelihood to fit the data to the phylogeny under some model of
evolutionary change (typically Brownian motion). The inclusion of a
scaling parameter, \(\lambda\), transforms the lengths of the internal
branches of the phylogeny to improve the fit, and this parameter
describes the degree of phylogenetic signal in the dataset (Pagel 1999;
Freckleton et al. 2002). Pagel's \(\lambda\) also has the appeal that it
may be included when estimating the association of traits in a
phylogenetic context, meaning that one may account for the degree of
phylogenetic signal while conducting phylogenetic regression or ANOVA
(see Freckleton et al. 2002). \hfill\break

Several studies have investigated the statistical properties of methods
for estimating phylogenetic signal under various conditions (e.g.,
Munkemuller et al. 2012; Pavoine and Ricotta 2012; Diniz-Filho et al.
2012; Molina-Venegas and Rodriguez 2017; see also Revell et al. 2008;
Revell 2010). These have largely focused on the ability of methods to
detect the presence of phylogenetic signal (i.e., type I and type II
error rates) under complex models of evolutionary change, across a range
of phylogeny sizes, and with varying degrees of phylogenetic uncertainty
or unresolved topologies. In terms of parameter estimation, Revell
(2010) found that regression parameters were accurately estimated when
\(\lambda\) was included during phylogenetic regression, and Munkmuller
et al.~(2012) demonstrated that estimates of phylogenetic signal
obtained using various measures generally increased when input levels of
phylogenetic signal were stronger. However, the precision of those
estimates could not be determined, because the input levels of
phylogenetic signal were simulated via a scaling factor (\(w\)) that was
not directly comparable to the measures of phylogenetic signal being
compared (see Munkemuller et al. 2012). One study (Boettiger et al.
2012) found that estimates of Pagel's \(\lambda\) displayed less
variation when data were simulated on a large phylogeny (\(N=281\)) as
compared to a small one (\(N=13\)), concluding that insufficient data
(i.e., the number of species) was the underlying cause of the increased
variation across parameter estimates. However, this conclusion assumes
that the precision in estimating \(\lambda\) remains constant across its
range (\(\lambda = 0 \to 1\)); an assumption that to date, has not been
verified. Thus, despite widespread use of Pagel's (1999) \(\lambda\) in
macroevolutionary studies, at present, we still lack a general
understanding of the precision with which \(\lambda\) can estimate
levels of phylogenetic signal in phenotypic datasets. \hfill\break

In this study, we evaluate the precision of Pagel's \(\lambda\) in
estimating known levels of phylogenetic signal in phenotypic data. We
use computer simulations with differing numbers of species, differently
shaped phylogenies, and differing input levels of phylogenetic signal,
to explore the degree to which \(\lambda\) correctly identifies known
levels of phylogenetic signal, and under what circumstances. We also
evaluate the precision of a standardized effect size (\(Z_K\)) based on
\(Kappa\) for comparison. Additionally, we use simulations to determine
how the inclusion of \(\lambda\) in phylogenetic regression and ANOVA
(i.e., PGLS) affects parameter estimation, and whether levels of
phylogenetic signal estimated in a PGLS framework are accurate. We then
survey the recent macroevolutionary literature for published papers
containing estimates of \(\lambda\) from empirical datasets, and compare
these empirical estimates to patterns gleaned from our computer
simulations. In general we find that while PGLS parameters (e.g.,
\(\beta\)) are accurately estimated with the inclusion of phylogenetic
signal, estimates of \(\lambda\) are not. We also find that estimates of
\(\lambda\) vary widely for a given input value of phylogenetic signal,
and that this variation is not constant across the range of input
signal, with decreased precision when phylogenetic signal is of
intermediate strength. In addition, the same \(\lambda_{est}\) may be
obtained from datasets containing vastly different input levels of
phylogenetic signal. By contrast, variation across effect sizes
(\(Z_K\)) obtained from \(Kappa\) is far more consistent across the
range of input values, and the precision of \(Z_K\) is generally
preferable to that of \(\lambda_{est}\). Further, because \(Z_K\) is a
standardized effect size, the strength of phylogenetic signal is more
readily interpretable, and may be compared across datasets. We conclude
that estimates of phylogenetic signal using Pagel's \(\lambda\) are
often innacurate, and thus interpreting strength of phylogenetic signal
in phenotypic datasets based on this measure is compromised. By
contrast, effect sizes obtained from \(Kappa\) hold promise for
characterizing phylogenetic signal, and for comparing the strength of
phylogenetic signal across datasets.

@@

Using the simulated phylogenies we estimated the phylogenetic signal in
each dataset using Pagel's \(\lambda\). Next, for the 1050 datasets at
each level of species richness (\(n\)), we assessed the relationship
between \(\lambda_{in}\) and \(\lambda_{est}\) using regression.
Additionally, the precision of \(\lambda\) was approximated by observing
the variation of \(\lambda_{est}\) obtained at each input level of
phylogenetic signal (\(\lambda_{in}\)). Finally, for comparison we
characterized the strength of phylogenetic signal in each dataset using
a standardized effect size (\(Z_K\): sensu Adams and Collyer 2016,
2019a) based on \(Kappa\). As suggested by Adams and Collyer (2019b),
the effect size for phylogenetic signal may be estimated as:
\(Z_K=\frac{K_{obs}-\mu_K}{\sigma_K}\), where \(K_{obs}\) was the
observed \(Kappa\), and \(\mu_K\) and \(\sigma_K\) were the mean and
standard deviation of the empirical sampling distribution of values
obtained from the permutation distribution. \(Z_K\) describes the
strength of phylogenetic signal as a standard deviate from its sampling
distribution, and thus directly measures the strength of signal in a
manner that is comparable across datasets. Variation in the set of
\(Z_K\) at each input level of phylogenetic signal was then calculated
as an estimate of precision in \(Z_K\). However, because \(Z_K\) differs
in scale from \(\lambda\), we used a linear normalization to standardize
\(Z_K\) to a uniform distribution (\(0\rightarrow1\)), and estimated the
precision of \(Z_K\) from the normalized values. \hfill\break

@@

Our first set of simulations revealed several patterns. First, the
relationship between \(\lambda_{est}\) and \(\lambda_{in}\) across the
range input levels of phylogenetic signal was \(\sim\beta=1.0\);
indicating that the average \(\lambda_{est}\) across datasets for a
given set of simulation condition correctly reflected input levels of
phylogenetic signal. However, as shown in Figure 1, the precision of
those estimates varied widely, and in several interesting ways.
Predictably, precision was worse at low levels of species richness,
where in many cases the set of \(\lambda_{est}\) spanned nearly the
entire range of possible values (e.g., \(n=32\); \(\lambda_{in}=0.5\):
range of \(\lambda_{est}= 0.0\to 0.985\)). Second, as species richness
increased, variation across estimates of \(\lambda\) decreased (Figure
1). This confirmed the pattern identified by Boettiger et al.~(2012) on
a small (\(n=13\)) versus a large (\(n=281\)) phylogeny, and
demonstrated that the trend of increasing precision with higher species
richness was general. Importantly however, our broader set of
simulations revealed that the precision of \(\lambda_{est}\) was not
uniform across all levels of phylogenetic signal. Specifically, we found
that variation in \(\lambda_{est}\) was highest at intermediate levels
of phylogenetic signal, and decreased at both lower and higher levels of
input signal (Figure 1). This implied that the precision in estimating
\(\lambda\) was worse at intermediate values, and improved as the levels
of phylogenetic signal were closer to \(\lambda_{in}=0\) (no
phylogenetic signal) or \(\lambda_{in}=1\) (Brownian motion). Notably,
even at large levels of species richness, the range of \(\lambda_{est}\)
still encompassed a substantial portion of possible values (e.g.,
\(n=512\); \(\lambda_{in}=0.5\): range of
\(\lambda_{est} = 0.32\to 0.68\)). Likewise, the same \(\lambda_{est}\)
could be obtained from datasets containing vastly different input levels
of phylogenetic signal (e.g., \(n=512\); \(\lambda_{est} = 0.5\); range
of \(\lambda_{in} = 0.25 \to 0.65\)). Taken together, these findings
reveal that \(\lambda_{est}\) does not precisely characterize observed
levels of phylogenetic signal in phenotypic datasets, and that
biological interpretations of the strength of phylogenetic signal based
on \(\lambda\) may be highly inaccurate. \hfill\break

@@

When \(\lambda\) was incorporated in PGLS regression and ANOVA (i.e.,
\(Y\sim{X}\)), we found much the same pattern as in the previous
simulations. Namely, the precision of \(\lambda_{est}\) varied inversely
with species richness; where greater precision was obtained at higher
levels of species richness (Figure 3). Likewise, the precision in
estimating \(\lambda\) was worse at intermediate values (Figure 3), and
improved as the levels of phylogenetic signal were closer to
\(\lambda_{in}=0\) (no phylogenetic signal) or \(\lambda_{in}=1\)
(Brownian motion). Generally, the spread of estimates was slightly
broader when \(\lambda\) was co-estimated with regression parameters in
PGLS regression (Figure 3), as compared to when \(\lambda\) was
estimated in cases only the dependent variable (Y) was considered
(Figure 1). Finally, found that regression parameters (\(\beta\)) were
accurately estimated when \(\lambda\) was included during phylogenetic
regression; a result which confirmed earlier findings of Revell (2010)
(see Supporting Information). \hfill\break

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\hypertarget{a-standardized-effect-size-for-evaluating-the-strength-of-phylogenetic-signal-and-why-lambda-is-not-appropriate}{%
\section{A Standardized Effect Size for Evaluating the Strength of
Phylogenetic Signal, and Why Lambda is not
Appropriate}\label{a-standardized-effect-size-for-evaluating-the-strength-of-phylogenetic-signal-and-why-lambda-is-not-appropriate}}

@@

\textbf{Keywords}: phylogenetic signal, effect size, Pagel's lambda
\hfill\break

\textbf{Short Title}: An Effect Size for Phylogenetic Signal
\hfill\break

@@

Several analytical tools have been developed to quantify phylogenetic
signal in phenotypic datasets, including measures of serial independence
(\(\mathbf{C}\): Abouheif 1999), autocorrelation estimates (\(I\):
Gittleman and Kot 1990), statistical ratios of trait variation relative
to what is expected given the phylogeny (\(Kappa\): Blomberg et al.
2003; Adams 2014a), and scaling parameters used in maximum likelihood
fitting of the data to the phylogeny (\(\lambda\): Pagel 1999), among
others (e.g., Klingenberg and Gidaszewski 2010). The statistical
properties of these methods -- namely type I error rates and power --
have also been investigated to determine when phylogenetic signal can be
detected and under what conditions (e.g., Munkemuller et al. 2012;
Pavoine and Ricotta 2012; Diniz-Filho et al. 2012; Adams 2014a;
Molina-Venegas and Rodriguez 2017; see also Revell et al. 2008; Revell
2010). One of the most widely used methods for characterizing
phylogenetic signal in macroevolutionary studies is Pagel's \(\lambda\)
(Pagel 1999). Here, maximum likelihood is used to fit the data to the
phylogeny under a Brownian motion model of evolution. A parameter
(\(\lambda\)) is included, which transforms the lengths of the internal
branches of the phylogeny to improve the fit (Pagel 1999; Freckleton et
al. 2002). Pagel's \(\lambda\), which ranges from \(0\to1\), is then
treated as a measure of phylogenetic signal; with values close to 0
signifying little phylogenetic signal, and values close to 1 indicating
that trait variation accumulates according to Brownian motion. Pagel's
\(\lambda\) also has the appeal that it may be included in phylogenetic
regression (PGLS) to account for the degree of phylogenetic signal in
comparative analyses (see Freckleton et al. 2002). \hfill\break

Evolutionary biologists commonly seek to describe the relative strength
of phylogenetic signal in phenotypic traits, to determine the extent to
which shared evolutionary history has influenced trait covariation among
taxa. This is often accomplished by interpreting empirical estimates of
\(\lambda\); with \(\lambda\approx0\) signifying `weak' phylogenetic
signal, and \(\lambda\approx1\) being interpreted as `strong'
phylogenetic signal (e.g., De Meester et al. 2019; Pintanel et al. 2019;
Su et al. 2019). Other approaches for interpreting \(\lambda\) are more
statistical, through the use of confidence intervals (Vandelook et al.
2019) or likelihood ratio tests that compare the observed model fit to
that obtained when \(\lambda=0\) or \(\lambda=1\) (Freckleton et al.
2002; Cooper et al. 2010; Bose et al. 2019). Likewise, qualitative
comparisons of \(\lambda\) across multiple phenotypic traits have also
been used to infer whether the strength of phylogenetic signal is
greater in one trait as compared to another (e.g., Liu et al. 2019; Bai
et al. 2019). Indeed, it seems intuitive to interpret the strength of
phylogenetic signal in this manner, as \(\lambda\) is a parameter on a
bounded scale (\(0\to1\)) for which interpretation of its extremal
points are well known (\(\lambda=0\) is no phylogenetic signal, while
\(\lambda=1\) corresponds to Brownian motion). However, equating values
of \(\lambda\) directly to the strength of phylogenetic signal presumes
two important statistical properties that have not been fully examined.
\hfill\break

First, it presumes that values of \(\lambda\) can be precisely
estimated, and that parameter estimates of \(\lambda\) are
representative of the underlying phylogenetic signal. Understanding the
precision in estimating levels of phylogenetic signal is paramount,
because biological inferences regarding the strength of phylogenetic
signal in phenotypic datasets requires high precision of its estimation.
One study (Boettiger et al. 2012) found that estimates of Pagel's
\(\lambda\) displayed less variation (i.e., greater precision) when data
were simulated on a large phylogeny (\(N=281\)) as compared to a small
one (\(N=13\)). From this observation it was concluded that insufficient
data (i.e., the number of species) was the underlying cause of the
increased variation across parameter estimates (Boettiger et al. 2012).
Indeed, such a pattern is common with statistical estimators, as summary
statistics and parameters are often more precise with greater sample
sizes (Cohen 1988). However, this conclusion also assumes that the
precision in estimating \(\lambda\) remains constant across its range
(\(\lambda = 0 \to 1\)); an assumption that to date, has not been
verified. Thus, despite widespread use of Pagel's (1999) \(\lambda\) in
macroevolutionary studies, at present, we still lack a general
understanding of the precision with which \(\lambda\) can estimate
levels of phylogenetic signal in phenotypic datasets. \hfill\break

Second, while \(\lambda\) is observed on a bounded scale (\(0\to1\)),
this does not \emph{de-facto} imply that the estimated values of this
parameter correspond to the actual strength of the underlying input
signal in the data. For this to be the case, \(\lambda\) must be a
statistical effect size. Effect sizes are a measure the magnitude of a
statistical effect in data, represented on a common scale (Glass 1976;
Cohen 1988). Effect sizes have widespread use in many areas of the
quantiative sciences, as they represent measures that may be readily
summarized across datasets (e.g., meta-analysis: Hedges and Olkin 1985;
Glass 1976; Arnqvist and Wooster 1995), or compared across datasets
(e.g., Adams and Collyer 2016, 2019a). Unfortunatley, not all
statistical parameters and test statistics are effect sizes, and thus
many summary measures must first be converted to standardized units
(i.e., an effect size) for meaningful comparison (see Rosenthal 1994).
As a consequence, it follows that only if \(\lambda\) is a statistical
effect size can comparisons of estimates across datasets be
interpretable. To date, it has not been determined whether \(\lambda\)
is an effect size for phylogenetic signal. \hfill\break

In this study, we evaluate the precision of Pagel's \(\lambda\) in
estimating known levels of phylogenetic signal in phenotypic data. We
use computer simulations with differing numbers of species, differently
shaped phylogenies, and differing input levels of phylogenetic signal,
to explore the degree to which \(\lambda\) correctly identifies known
levels of phylogenetic signal, and under what circumstances. We then
derive a standardized effect size for phylogenetic signal, and apply the
concept to two common measures of phylogenetic signal: \(\lambda\)
(\(Z_{\lambda}\)) and \(Kappa\) (\(Z_K\)). In general we find that while
PGLS parameters (e.g., \(\beta\)) are accurately estimated with the
inclusion of phylogenetic signal, estimates of \(\lambda\) are not. We
also find that estimates of \(\lambda\) vary widely for a given input
value of phylogenetic signal, and that this variation is not constant
across the range of input signal, with decreased precision when
phylogenetic signal is of intermediate strength. Additionally, the same
\(\lambda_{est}\) may be obtained from datasets containing vastly
different input levels of phylogenetic signal. Likewise, the precision
of \(Z_{\lambda}\) is less consistent than that observed with \(Z_K\),
across the range of input values, implying that \(Z_K\) is a more robust
effect size measure. Further, because \(Z_K\) is a standardized effect
size, the strength of phylogenetic signal is more readily interpretable,
and may be compared across datasets. We conclude that estimates of
phylogenetic signal using Pagel's \(\lambda\) are often inaccurate, and
thus interpreting strength of phylogenetic signal in phenotypic datasets
based on this measure is compromised. By contrast, effect sizes obtained
from \(Kappa\) hold promise for characterizing phylogenetic signal, and
for comparing the strength of phylogenetic signal across datasets.

\hypertarget{methods-and-results}{%
\section{Methods and Results}\label{methods-and-results}}

-Lambda is not precise: holds in estimates, and PGLSregression
-Precision varies with N (duh) but also WITH INPUT! -same input on
different N, different lambda.est -same lambda.est from different input
-Boettiger example: add small tips, greatly change lambda\ldots{}
-Conclusion: Lambda does not quantify strength of phylogenetic signal as
is often assumed

-Empirical examples: how interpretation can get folks ito trouble.

-A proposed Effect size for the strength of physig -Derivation of effect
size (expand on Adams and Collyer 2019 suggestion that an effect size
for phylogenetic signal is needed. The `gold standard' of these is a
standaredized effect size: (following the meta-analytic literature
beginning with Glass 1976). In other words, a Z-score. So, how does Z
work when based on lambda? On kappa? - Z-score. could be Lambda or
Kappa. Show it is Kappa -Comparing the strength of physig - two sample
Z-score

-Conclusions and Implications

\hypertarget{lambda-is-not-precise}{%
\subsection{\texorpdfstring{\(\lambda\) is not
Precise}{\textbackslash lambda is not Precise}}\label{lambda-is-not-precise}}

\hypertarget{lambda-does-not-measure-phylogenetic-signal}{%
\subsection{Lambda does not measure phylogenetic
signal}\label{lambda-does-not-measure-phylogenetic-signal}}

\hypertarget{an-effect-size-for-physig}{%
\subsection{An effect size for Physig}\label{an-effect-size-for-physig}}

@@

Using the simulated phylogenies we estimated the phylogenetic signal in
each dataset using Pagel's \(\lambda\). Next, for the 1050 datasets at
each level of species richness (\(n\)), we assessed the relationship
between \(\lambda_{in}\) and \(\lambda_{est}\) using regression.
Additionally, the precision of \(\lambda\) was approximated by observing
the variation of \(\lambda_{est}\) obtained at each input level of
phylogenetic signal (\(\lambda_{in}\)). Finally, for comparison we
characterized the strength of phylogenetic signal in each dataset using
a standardized effect size (\(Z_K\): sensu Adams and Collyer 2016,
2019a) based on \(Kappa\). As suggested by Adams and Collyer (2019b), an
effect size for phylogenetic signal may be estimated as:
\(Z_K=\frac{K_{obs}-\mu_K}{\sigma_K}\), where \(K_{obs}\) was the
observed \(Kappa\), and \(\mu_K\) and \(\sigma_K\) were the mean and
standard deviation of the empirical sampling distribution of values
obtained from the permutation distribution. \(Z_K\) describes the
strength of phylogenetic signal as a standard deviate from its sampling
distribution, and thus directly measures the strength of signal in a
manner that is comparable across datasets. Variation in the set of
\(Z_K\) at each input level of phylogenetic signal was then calculated
as an estimate of precision in \(Z_K\). However, because \(Z_K\) differs
in scale from \(\lambda\), we used a linear normalization to standardize
\(Z_K\) to a uniform distribution (\(0\rightarrow1\)), and estimated the
precision of \(Z_K\) from the normalized values. \hfill\break

@@

Our first set of simulations revealed several patterns. First, the
relationship between \(\lambda_{est}\) and \(\lambda_{in}\) across the
range input levels of phylogenetic signal was \(\beta\sim1.0\);
indicating that the average \(\lambda_{est}\) across datasets for a
given simulation condition correctly reflected the input levels of
phylogenetic signal. However, as shown in Figure 1, the precision of
those estimates varied widely, and in several interesting ways.
Predictably, precision was worse at low levels of species richness,
where in many cases the set of \(\lambda_{est}\) spanned nearly the
entire range of possible values (e.g., \(n=32\); \(\lambda_{in}=0.5\):
range of \(\lambda_{est}= 0.0\to 0.985\)). Second, as species richness
increased, variation across estimates of \(\lambda\) decreased (Figure
1). This confirmed the pattern identified by Boettiger et al.~(2012) on
a small (\(n=13\)) versus a large (\(n=281\)) phylogeny, and
demonstrated that the trend of increasing precision with higher species
richness was general; adhering to parametric statistical theory.
Importantly however, our broader set of simulations revealed that the
precision of \(\lambda_{est}\) was not uniform across all levels of
phylogenetic signal. Specifically, we found that variation in
\(\lambda_{est}\) was highest at intermediate levels of phylogenetic
signal, and decreased at both lower and higher levels of input signal
(Figure 1). This implied that the precision in estimating \(\lambda\)
was worse at intermediate values, and improved as the levels of
phylogenetic signal were closer to \(\lambda_{in}=0\) (no phylogenetic
signal) or \(\lambda_{in}=1\) (Brownian motion). Notably, even at large
levels of species richness, the range of \(\lambda_{est}\) still
encompassed a substantial portion of possible values (e.g., \(n=512\);
\(\lambda_{in}=0.5\): range of \(\lambda_{est} = 0.32\to 0.68\)).
Likewise, the same \(\lambda_{est}\) could be obtained from datasets
containing vastly different input levels of phylogenetic signal (e.g.,
\(n=512\); \(\lambda_{est} = 0.5\); range of
\(\lambda_{in} = 0.25 \to 0.65\)). Taken together, these findings reveal
that \(\lambda_{est}\) does not precisely characterize observed levels
of phylogenetic signal in phenotypic datasets, and that biological
interpretations of the strength of phylogenetic signal based on
\(\lambda\) may be highly inaccurate. \hfill\break

@@

When \(\lambda\) was incorporated in PGLS regression and ANOVA (i.e.,
\(Y\sim{X}\)), we found much the same pattern as in our earlier
simulations. Namely, the precision of \(\lambda_{est}\) covaried with
species richness; where greater precision was obtained at higher levels
of species richness (Figure 3). Likewise, the precision in estimating
\(\lambda\) was worse at intermediate values (Figure 3), and improved as
the levels of phylogenetic signal were closer to \(\lambda_{in}=0\) (no
phylogenetic signal) or \(\lambda_{in}=1\) (Brownian motion). Generally,
the spread of estimates was slightly broader when \(\lambda\) was
co-estimated with regression parameters in PGLS regression (Figure 3),
as compared to when \(\lambda\) was estimated for only the dependent
variable (Figure 1). Finally, we found that regression parameters
(\(\beta\)) were accurately estimated when \(\lambda\) was included
during phylogenetic regression; a result which confirmed earlier
findings of Revell (2010) (see Supporting Information). \hfill\break

@@

\leavevmode\hypertarget{ref-Arnqvist1995}{}%
Arnqvist, G., and D. Wooster. 1995. Meta-analysis: Synthesizing research
findings in ecology and evolution. Trends in Ecology and Evolution
10:236--240.

\leavevmode\hypertarget{ref-Bai2019}{}%
Bai, K., S. Lv, S. Ning, D. Zeng, Y. Guo, and B. Wang. 2019. Leaf
nutrient concentrations associated with phylogeny, leaf habit and soil
chemistry in tropical karst seasonal rainforest tree species. Plant and
Soil 434:305--326.

@@

\leavevmode\hypertarget{ref-Bose2019}{}%
Bose, R., B. R. Ramesh, R. Pélissier, and F. Munoz. 2019. Phylogenetic
diversity in the western ghats biodiversity hotspot reflects
environmental filtering and past niche diversification of trees. Journal
of Biogeography 46:145--157.

@@

\leavevmode\hypertarget{ref-Cohen1988}{}%
Cohen, J. 1988. Statistical power analysis for the behavioral sciences.
Routledge.

\leavevmode\hypertarget{ref-Cooper2010}{}%
Cooper, N., W. Jetz, and R. P. Freckleton. 2010. Phylogenetic
comparative approaches for studying niche conservatism. Journal of
Evolutionary Biology 23:2529--2539.

\leavevmode\hypertarget{ref-DeMeester2019}{}%
De Meester, G., K. Huyghe, and R. Van Damme. 2019. Brain size, ecology
and sociality: A reptilian perspective. Biological Journal of the
Linnean Society 126:381--391.

@@

\leavevmode\hypertarget{ref-Glass1976}{}%
Glass, G. V. 1976. Primary, secondary, and meta-analysis of research.
Educational Researcher 5:3--8.

@@

\leavevmode\hypertarget{ref-HedgesOlkin1985}{}%
Hedges, L. V., and I. Olkin. 1985. Statistical methods for
meta-analysis. Elsevier.

@@

\leavevmode\hypertarget{ref-Liu2019}{}%
Liu, H., C. P. Osborne, D. Yin, R. P. Freckleton, G. Jiang, and M. Liu.
2019. Phylogeny and ecological processes influence grass coexistence at
different spatial scales within the steppe biome. Oecologia 191:25--38.

@@

\leavevmode\hypertarget{ref-Pintanel2019}{}%
Pintanel, P., M. Tejedo, S. R. Ron, G. A. Llorente, and A.
Merino-Viteri. 2019. Elevational and microclimatic drivers of thermal
tolerance in andean pristimantis frogs. Journal of Biogeography
46:1664--1675.

@@

\leavevmode\hypertarget{ref-Rosenthal1994}{}%
Rosenthal, R. 1994. The handbook of research synthesis. Pp. 231--244
\emph{in} L. V. Cooper H Hedges, ed. Russell Sage Foundation.

\leavevmode\hypertarget{ref-Su2019}{}%
Su, G., S. Villéger, and S. Brosse. 2019. Morphological diversity of
freshwater fishes differs between realms, but morphologically extreme
species are widespread. Global ecology and biogeography 28:211--221.

\leavevmode\hypertarget{ref-Vandelook2019}{}%
Vandelook, F., S. Janssens, P. Gijbels, E. Fischer, W. Van den Ende, O.
Honnay, and S. Abrahamczyk. 2019. Nectar traits differ between
pollination syndromes in balsaminaceae. Annals of Botany 124:269--279.
